---
title: "T-Test Simulations"
author: "Sam Pritchard"
date: "December 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(dplyr)
require(ggplot2)
require(lubridate)
```

## Means are 2 standard deviations apart

```{r, echo=FALSE}


rand.norm1 <- rnorm(100)
rand.norm2 <- (rnorm(100)+2)

conf.df <- data.frame()
for(i in 1:99){
  rand1 <- rand.norm1[1:(i+1)]
  rand2 <- rand.norm2[1:(i+1)]
  t.test.i <- t.test(rand1, rand2)
  conf.int.i <- t.test.i$conf.int
  conf.df <- rbind(conf.df, conf.int.i)
}
conf.df$deg.free <- seq(nrow(conf.df))
colnames(conf.df) <- c("low.bound", "high.bound", "deg.free")
print(head(conf.df))
rplot <- ggplot(conf.df, aes(x=deg.free)) +
  geom_point(aes(y=low.bound))+
  geom_point(aes(y=high.bound))+
  geom_segment(x=0, xend=99, y=0, yend=0, color="yellow")
print(rplot)
  
  


```

## One Standard Deviation Higher

```{r pressure, echo=FALSE}
rand.norm1 <- rnorm(100)
rand.norm2 <- (rnorm(100)+1)

conf.df <- data.frame()
for(i in 1:99){
  rand1 <- rand.norm1[1:(i+1)]
  rand2 <- rand.norm2[1:(i+1)]
  t.test.i <- t.test(rand1, rand2)
  conf.int.i <- t.test.i$conf.int
  conf.df <- rbind(conf.df, conf.int.i)
}
conf.df$deg.free <- seq(nrow(conf.df))
colnames(conf.df) <- c("low.bound", "high.bound", "deg.free")
print(head(conf.df))
rplot <- ggplot(conf.df, aes(x=deg.free)) +
  geom_point(aes(y=low.bound))+
  geom_point(aes(y=high.bound))+
  geom_segment(x=0, xend=99, y=0, yend=0, color="yellow")
print(rplot)
```

## 1/5 of a standard deviation higher

```{r, echo=FALSE}
rand.norm1 <- rnorm(100)
rand.norm2 <- (rnorm(100)+.2)

conf.df <- data.frame()
for(i in 1:99){
  rand1 <- rand.norm1[1:(i+1)]
  rand2 <- rand.norm2[1:(i+1)]
  t.test.i <- t.test(rand1, rand2)
  conf.int.i <- t.test.i$conf.int
  conf.df <- rbind(conf.df, conf.int.i)
}
conf.df$deg.free <- seq(nrow(conf.df))
colnames(conf.df) <- c("low.bound", "high.bound", "deg.free")
print(head(conf.df))
rplot <- ggplot(conf.df, aes(x=deg.free)) +
  geom_point(aes(y=low.bound))+
  geom_point(aes(y=high.bound))+
  geom_segment(x=0, xend=99, y=0, yend=0, color="yellow")
print(rplot)
