---
title: "Daily Sales T-Test"
author: "Sam Pritchard"
date: "December 26, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(dplyr)
require(ggplot2)
require(lubridate)

data17 <- read.csv("Detailed Sales Report 17.csv", stringsAsFactors = FALSE)
data16 <- read.csv("Detailed Sales Report 16.csv", stringsAsFactors = FALSE)

data.both <- rbind(data17, data16)
data.both$Total.Sales <- as.numeric(data.both$Total.Sales)
data.both <- filter(data.both, !is.na(Total.Sales)) #removes the sums that had $ signs in them
print(paste("sum of Total.Sales is", sum(data.both$Total.Sales)))
data.both$Date.Sold <- mdy_hm(data.both$Date.Sold)
data.both$Date <- as_date(data.both$Date.Sold)
data.both$Year <- year(data.both$Date.Sold)
data.both$Month <- month(data.both$Date.Sold)
data.both$Department <- trimws(data.both$Department)
data.both$Category <- trimws(data.both$Category)
data.both$Supplier <- trimws(data.both$Supplier)
data.both$Item <- trimws(data.both$Item)
data.both$Year.Month <- as.numeric(paste0(substr(data.both$Year,3,4), data.both$Month))
data.both$Year.Month <- as.factor(data.both$Year.Month)

```

## Sellers Publishing

```{r, echo=FALSE}
sellers.pub <- filter(data.both, Supplier == "SELLERS PUBLISHING, INC.")
sellers.pub.agg <- aggregate(Total.Sales ~ Date + Month + Year, sellers.pub, sum)
hist.plot <- hist(sellers.pub.agg$Total.Sales, breaks=20)
print(hist.plot)

sellers.pub.agg17 <- filter(sellers.pub.agg, Month >= 6, Month <= 9, Year == 2017)
sellers.pub.agg16 <- filter(sellers.pub.agg, Month >= 6, Month <= 9, Year == 2016)
hist.plot17 <- hist(sellers.pub.agg17$Total.Sales, breaks=20)
print(hist.plot17)

hist.plot16 <- hist(sellers.pub.agg16$Total.Sales, breaks=20)
print(hist.plot16)

#print(sellers.pub.agg16)
#print(head(sellers.pub.agg, 15))
#line.sup.agg.all <- aggregate(Total.Sales ~ Date, data.both.supplier, sum)
```

### Example of AB Test with a T Test showing means that are not equal with 95% certainty
Starting around day 20 but definitely by 25 days it's clear that the mean of group 2 will be below that of group 1.  The line graph with monthly totals bears this out.

```{r, echo=FALSE}

rand.norm1 <- sellers.pub.agg17$Total.Sales
rand.norm2 <- sellers.pub.agg16$Total.Sales

conf.df <- data.frame()
for(i in 1:120){
  rand1 <- rand.norm1[1:(i+1)]
  rand2 <- rand.norm2[1:(i+1)]
  t.test.i <- t.test(rand1, rand2)
  conf.int.i <- t.test.i$conf.int
  conf.df <- rbind(conf.df, conf.int.i)
}
conf.df$deg.free <- seq(nrow(conf.df))
colnames(conf.df) <- c("low.bound", "high.bound", "deg.free")
print(head(conf.df))
rplot <- ggplot(conf.df, aes(x=deg.free)) +
  geom_point(aes(y=low.bound))+
  geom_point(aes(y=high.bound))+
  geom_segment(x=0, xend=119, y=0, yend=0, color="yellow")
print(rplot)
```


### Three Levels of Confidence AB Test

```{r, echo=FALSE}

data.b.comparison <- (sellers.pub.agg17$Total.Sales)
data.a.baseline <- sellers.pub.agg16$Total.Sales
conf.df <- data.frame()

for(i in 1:120){
  b.comp <- data.b.comparison[1:(i+1)]
  a.base <- data.a.baseline[1:(i+1)]
  conf.int95.i <- t.test(b.comp, a.base, conf.level = 0.95)$conf.int
  conf.int85.i <- t.test(b.comp, a.base, conf.level = 0.85)$conf.int
  conf.int75.i <- t.test(b.comp, a.base, conf.level = 0.75)$conf.int
  three.conf.int.i <- c(conf.int95.i, conf.int85.i, conf.int75.i)
  conf.df <- rbind(conf.df, three.conf.int.i)
}
```

```{r, echo=FALSE}
conf.df$deg.free <- seq(nrow(conf.df))
colnames(conf.df) <- c("low95", "high95", "low85", "high85", "low75", "high75", "deg.free")
print(head(conf.df))
```


```{r, echo=FALSE, fig.height=3, fig.width=3}

# create dark green arrow down

arrow.dgreen.down <- ggplot(data=data.frame("x"= 1, "y"=1)) +
  theme(panel.background = element_rect(fill = "#FFFFFF", color="black"), 
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank()) + 
  xlim(0,2) +
  ylim(0,2) +
geom_segment(x=1, xend=1, y=0, yend=2, color="#003300", size=2) +
geom_segment(x=1, xend=1.5, y=0, yend=.5, color="#003300", size=2) +
geom_segment(x=0.5, xend=1, y=0.5, yend=0, color="#003300", size=2)

# create dark green arrow up

arrow.dgreen.up <- ggplot(data=data.frame("x"= 1, "y"=1)) +
  theme(panel.background = element_rect(fill = "#FFFFFF", color="black"), 
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank()) + 
  xlim(0,2) +
  ylim(0,2) +
geom_segment(x=1, xend=1, y=0, yend=2, color="#003300", size=2) +
geom_segment(x=1, xend=1.5, y=2, yend=1.5, color="#003300", size=2) +
geom_segment(x=0.5, xend=1, y=1.5, yend=2, color="#003300", size=2)

# create light green arrow down

arrow.lgreen.down <- ggplot(data=data.frame("x"= 1, "y"=1)) +
  theme(panel.background = element_rect(fill = "#FFFFFF", color="black"), 
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank()) + 
  xlim(0,2) +
  ylim(0,2) +
geom_segment(x=1, xend=1, y=0, yend=2, color="#33CC00", size=2) +
geom_segment(x=1, xend=1.5, y=0, yend=.5, color="#33CC00", size=2) +
geom_segment(x=0.5, xend=1, y=0.5, yend=0, color="#33CC00", size=2)

# create light green arrow up

arrow.lgreen.up <- ggplot(data=data.frame("x"= 1, "y"=1)) +
  theme(panel.background = element_rect(fill = "#FFFFFF", color="black"), 
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank()) + 
  xlim(0,2) +
  ylim(0,2) +
geom_segment(x=1, xend=1, y=0, yend=2, color="#33CC00", size=2) +
geom_segment(x=1, xend=1.5, y=2, yend=1.5, color="#33CC00", size=2) +
geom_segment(x=0.5, xend=1, y=1.5, yend=2, color="#33CC00", size=2)

# create yellow green arrow down

arrow.ygreen.down <- ggplot(data=data.frame("x"= 1, "y"=1)) +
  theme(panel.background = element_rect(fill = "#FFFFFF", color="black"), 
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank()) + 
  xlim(0,2) +
  ylim(0,2) +
geom_segment(x=1, xend=1, y=0, yend=2, color="#CCFF33", size=2) +
geom_segment(x=1, xend=1.5, y=0, yend=.5, color="#CCFF33", size=2) +
geom_segment(x=0.5, xend=1, y=0.5, yend=0, color="#CCFF33", size=2)

# create yellow green arrow up

arrow.ygreen.up <- ggplot(data=data.frame("x"= 1, "y"=1)) +
  theme(panel.background = element_rect(fill = "#FFFFFF", color="black"), 
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank()) + 
  xlim(0,2) +
  ylim(0,2) +
geom_segment(x=1, xend=1, y=0, yend=2, color="#CCFF33", size=2) +
geom_segment(x=1, xend=1.5, y=2, yend=1.5, color="#CCFF33", size=2) +
geom_segment(x=0.5, xend=1, y=1.5, yend=2, color="#CCFF33", size=2)

# print a question mark
q.mark <- ggplot(data=data.frame("x"= 1, "y"=1)) +
  xlim(0,2) +
  ylim(0,2) +
  geom_text(aes(x=x, y=y,label="?"), size=50) +
  theme(panel.background = element_rect(fill = "#FFFFFF", color="black"), 
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank())

# determine which arrow should be printed

if(tail(conf.df$low95,1) <0 & 
   tail(conf.df$high95,1)<0){
  print(arrow.dgreen.down)
    } else if(tail(conf.df$low95,1) >0 & 
              tail(conf.df$high95,1)>0){
      print(arrow.dgreen.up)
    } else if(tail(conf.df$low85,1) <0 & 
              tail(conf.df$high85,1)<0){
      print(arrow.lgreen.down)
    } else if(tail(conf.df$low85,1) >0 & 
              tail(conf.df$high85,1)>0){
      print(arrow.lgreen.up)
    } else if(tail(conf.df$low75,1) <0 & 
              tail(conf.df$high75,1)<0){
      print(arrow.ygreen.down)
    } else if(tail(conf.df$low75,1) >0 & 
              tail(conf.df$high75,1)>0){
      print(arrow.ygreen.up)
    } else {
      print(q.mark)
    }

#print(q.mark)




```


```{r, echo=FALSE}
three.plot <- ggplot(conf.df, aes(x=deg.free)) +
  geom_point(aes(y=low95))+
  geom_point(aes(y=high95))+
  geom_point(aes(y=low85))+
  geom_point(aes(y=high85))+
  geom_point(aes(y=low75))+
  geom_point(aes(y=high75))+
  geom_ribbon(aes(ymin=low95, ymax=high95), fill="#003300")+
  geom_ribbon(aes(ymin=low85, ymax=high85), fill="#33CC00")+
  geom_ribbon(aes(ymin=low75, ymax=high75), fill="#CCFF33")+
  geom_segment(x=0, xend=119, y=0, yend=0, color="yellow", size=2)
print(three.plot)


```

## Acomo Jewelry

```{r, echo=FALSE}

acomo <- filter(data.both, Supplier == "ACOMO JEWELRY")
acomo.agg <- aggregate(Total.Sales ~ Date + Month + Year, acomo, sum)
#hist.plot <- hist(sellers.pub.agg$Total.Sales, breaks=20)
#print(hist.plot)

acomo.agg17 <- filter(acomo.agg, Month >= 6, Month <= 9, Year == 2017)
acomo.agg16 <- filter(acomo.agg, Month >= 6, Month <= 9, Year == 2016)
acomo.plot17 <- hist(acomo.agg17$Total.Sales, breaks=20)
print(acomo.plot17)

acomo.plot16 <- hist(acomo.agg16$Total.Sales, breaks=20)
print(acomo.plot16)

```

### Example of AB Test with a T Test showing means that COULD BE equal with 95% certainty (Acomo Jewelry)

```{r, echo=FALSE}
rand.norm1 <- acomo.agg17$Total.Sales
rand.norm2 <- acomo.agg16$Total.Sales

conf.df <- data.frame()
for(i in 1:120){
  rand1 <- rand.norm1[1:(i+1)]
  rand2 <- rand.norm2[1:(i+1)]
  t.test.i <- t.test(rand1, rand2)
  conf.int.i <- t.test.i$conf.int
  conf.df <- rbind(conf.df, conf.int.i)
}
conf.df$deg.free <- seq(nrow(conf.df))
colnames(conf.df) <- c("low.bound", "high.bound", "deg.free")
print(head(conf.df))
acomo.ab <- ggplot(conf.df, aes(x=deg.free)) +
  geom_point(aes(y=low.bound))+
  geom_point(aes(y=high.bound))+
  geom_segment(x=0, xend=119, y=0, yend=0, color="yellow")+
  ylim(c(-500, 500))
print(acomo.ab)
