---
title: "Supplier Deep Dive - FIREFLY"
author: "Allocate Analytics"
date: "January 26, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(dplyr)
require(ggplot2)
require(lubridate)
require(knitr)
require(fpp2)

supplier.to.dive <- "FIREFLY" #use all caps.  They're all caps in data

#contents 2019

#1 Autoplot of data for selected time period to show time period and a great viz out of the gate
#2 text info about the products and the suppliers broken down

#3 Text about the 80-20 rule - which suppliers' products generating the most sales and the least

#####
begin.date <- as.Date("2015-01-01")
freemium.end.date <- as.Date("2018-12-31") ##### Date to end the data 
#freemium.end.date <- as.Date("2099-12-31") #### removes no dates but does remove NAs
#####

#next if-else
if(file.exists(paste0("data/sales.data.cache", Sys.Date(), ".csv"))){
  data.clean <- read.csv(paste0("data/sales.data.cache", Sys.Date(), ".csv"), stringsAsFactor = FALSE)
} else {
  
import.jh.sql.connect <- function(db.name.in.sql.server){
  library(odbc)
  library(DBI)
  
  con <- DBI::dbConnect(odbc::odbc(),
                        Driver = "SQL Server",
                        Server = "LAPTOP-JHRVTF04\\SQLEXPRESS",
                        Database = db.name.in.sql.server,
                        Trusted_Connection = "True")
  con
}
import.jh.detailed.sales <- function(){
  joined.df <- DBI::dbGetQuery(con,'
                                SELECT TransactionEntry.ItemID, TransactionEntry.Price, 
                                 TransactionEntry.TransactionTime, TransactionEntry.Quantity, 
                                  TransactionEntry.TransactionNumber, Item.Description, 
                                 Department.Name AS "Department", Category.Name AS "Category", 
                                 SupplierName AS "Supplier", Cashier.Name AS "CashierName", 
                                 Register.Number AS "Register", Register.Description AS "RegLocation"
                                 FROM TransactionEntry
                                 
                                 JOIN Item ON TransactionEntry.ItemID = Item.ID
                                 JOIN Department ON Item.DepartmentID = Department.ID
                                 JOIN Category ON Item.CategoryID = Category.ID
                                 JOIN Supplier ON Item.SupplierID = Supplier.ID
                                 JOIN [Transaction] ON TransactionEntry.TransactionNumber = [Transaction].TransactionNumber
                                 JOIN Batch ON [Transaction].BatchNumber = Batch.BatchNumber
                                 JOIN Register ON Batch.RegisterID = Register.ID
                                 JOIN Cashier ON [Transaction].CashierID = Cashier.ID')
  joined.df
  }
clean.jh.detailed.sales <- function(sql.df){
  library(dplyr)
  library(lubridate)
    
    sql.df <- sql.df %>%
      rename(Sold.Price = Price, Cashier = CashierName, Date.Sold = TransactionTime,
             Qty.Sold = Quantity, Transaction = TransactionNumber) %>%
      mutate(Total.Sales = Qty.Sold*Sold.Price) %>%
      select(Department, Category, Supplier, ItemID, Description, Qty.Sold, Sold.Price, 
             Total.Sales, Transaction, Date.Sold, Register, Cashier)
    
    sql.df$Date.Sold <- ymd_hms(sql.df$Date.Sold)
    sql.df$Year <- year(sql.df$Date.Sold)
    sql.df$Month <- month(sql.df$Date.Sold)
    sql.df$Department <- trimws(sql.df$Department)
    sql.df$Category <- trimws(sql.df$Category)
    sql.df$Supplier <- trimws(sql.df$Supplier)
    sql.df$Item <- trimws(sql.df$Item)
    #print(head(sql.df))
    sql.df$Dept.By.Year <- paste(sql.df$Department, sql.df$Year)
    sql.df$Categ.By.Year <- paste(sql.df$Category, sql.df$Year)
    sql.df
}

con <- import.jh.sql.connect("WHALESTALE")
new.df <- import.jh.detailed.sales() # uses con but not as argument
data.clean <- clean.jh.detailed.sales(new.df)

write.csv(data.clean, paste0("data/sales.data.cache", Sys.Date(), ".csv"), row.names = FALSE)
}

#read in another function independent of caching
exploratory.jh.time.series <- function(clean.df, freq = 365){
  require(lubridate)
  require(dplyr)
  clean.df <- arrange(clean.df, Date.Sold)
  clean.df$Day <- date(clean.df$Date.Sold) # df should have been arranged in cleaning step
  start.year <- year(clean.df$Day)[1]
  if(freq == 365){
    start.day <- date(head(clean.df$Day,1)) - floor_date(head(clean.df$Day,1), unit = "year")+1 # subtracts earliest day from first day of year plus one
    sales.agg <- aggregate(Total.Sales ~ Day, clean.df, sum)
    all.dates <- seq.Date(from = as.Date(min(sales.agg$Day, na.rm = TRUE)), to = as.Date(max(sales.agg$Day, na.rm = TRUE)),by = 1)
    sales.agg.all <- left_join(data.frame(Day = all.dates), sales.agg)
    sales.ts <- ts(sales.agg.all$Total.Sales, start = c(start.year, start.day), frequency = 365)
  }
  if(freq == 12){
    start.month <- month(head(clean.df$Month,1))
    sales.agg <- aggregate(Total.Sales ~ Month + Year, clean.df, sum)
    #print(head(sales.agg, 25))
    sales.agg.all <- left_join(sales.agg, data.frame(Month = 1:12))
    sales.ts <- ts(sales.agg.all$Total.Sales, start = c(start.year, start.month), frequency = 12)
  }
  sales.ts[is.na(sales.ts)] <- 0
  
  sales.ts
}

data.clean <- filter(data.clean, Date.Sold <= freemium.end.date, Date.Sold >= begin.date) ##### check
data.both <- data.clean
data.dive <- filter(data.clean, Supplier == supplier.to.dive)
#dept.agg <- aggregate(Total.Sales ~ Dept.By.Year + Department + Categ.By.Year + Category + Year, data.both, sum)

#category table building for current year ("cy")
data.dive$Cat.By.Year <- paste(data.dive$Category, data.dive$Year)
cat.agg <- aggregate(Total.Sales ~ Cat.By.Year + Category + Year, data.dive, sum)
cy <- year(freemium.end.date)
py <- year(freemium.end.date)-1
cat.agg.cy <- filter(cat.agg, Year == cy)
cat.cy.sum <- sum(cat.agg.cy$Total.Sales)
cat.agg.cy <- mutate(cat.agg.cy, "Perc.Whole" = round((Total.Sales/cat.cy.sum)*100, 2))
cat.agg.cy <- arrange(cat.agg.cy, desc(Total.Sales))

cat.unit <- aggregate(Total.Sales ~ Cat.By.Year + Category + Year, data.dive, length)

#product table building for current year ("cy")
data.dive$Product.By.Year <- paste(data.dive$Description, data.dive$Year)
product.agg <- aggregate(Total.Sales ~ Product.By.Year + Description + Year, data.dive, sum)
cy <- year(freemium.end.date)
py <- year(freemium.end.date)-1
product.agg.cy <- filter(product.agg, Year == cy)
product.cy.sum <- sum(product.agg.cy$Total.Sales)
product.agg.cy <- mutate(product.agg.cy, "Perc.Whole" = round((Total.Sales/product.cy.sum)*100, 2))
product.agg.cy <- arrange(product.agg.cy, desc(Total.Sales))

#supplier calc retained to avoid errors from variable dependencies
data.both.supplier <- data.both
data.both.supplier$Supp.By.Year <- paste(data.both.supplier$Supplier, data.both.supplier$Year)
supplier.agg <- aggregate(Total.Sales ~ Supp.By.Year + Supplier + Year, data.both.supplier, sum)
cy <- year(freemium.end.date)
py <- year(freemium.end.date)-1
supplier.agg.cy <- filter(supplier.agg, Year == cy)
supp.cy.sum <- sum(supplier.agg.cy$Total.Sales)
supplier.agg.cy <- mutate(supplier.agg.cy, "Perc.Whole" = round((Total.Sales/supp.cy.sum)*100, 2))
supplier.agg.cy <- arrange(supplier.agg.cy, desc(Total.Sales))

prod.uniq <- length(unique(data.dive$ItemID))
cat.uniq <- length(unique(data.dive$Category))
dept.uniq <- length(unique(data.dive$Department))
```


###This report provides an in-depth look at sales of products from `r supplier.to.dive`.

Included are the following:

*	Bar graph of sales from `r supplier.to.dive` by year

*	Line graph of sales from `r supplier.to.dive` by month

*	Line graph of sales by category

*	Tables of sales by category (in dollars and units sold)

*	Bar graph of top `r supplier.to.dive` products comparing sales by year

* Table of sales by product comparing `r cy` with `r py` for top products

Note: this report relies on data from `r as.Date(min(data.clean$Date.Sold, na.rm = TRUE))` to `r as.Date(max(data.clean$Date.Sold, na.rm = TRUE))`. 



```{r, allin, echo = FALSE, warning=FALSE, message=FALSE, fig.height=3}
allin.agg <- aggregate(Total.Sales ~ Year, cat.agg, sum)

#####just a test
#allin.agg <- filter(allin.agg, Year >= 2018)

#####
years.incl <- unique(allin.agg$Year)  # important because picking color palettes manually for lines

all.ts <- exploratory.jh.time.series(data.dive, freq = 12)

if(length(years.incl) == 1){

  man.pal <- c("#67a9cf") #manual palette
  
  all.bar <- ggplot(data = allin.agg, aes(y = Total.Sales, x = factor(Year), fill = factor(Year))) + 
    geom_bar(stat = "identity") + scale_y_continuous(labels = scales::dollar) + 
    scale_fill_manual(name = "Year", values = man.pal) + theme_dark()+
    labs(x = "Year", y = "Sales") + 
    theme(legend.position="none")

year1.ts <- all.ts

all.line <- autoplot(all.ts) + autolayer(year1.ts, color = man.pal[1], size = 3) + theme_dark()+ 
  labs(y = "Sales", title = "Total Sales from Selected Supplier by Month") +
  scale_y_continuous(labels = scales::dollar)

}

if(length(years.incl) == 2){

  man.pal <- c("#f7f7f7", "#67a9cf") #manual palette
  
  all.bar <- ggplot(data = allin.agg, aes(y = Total.Sales, x = factor(Year), fill = factor(Year))) + 
  geom_bar(stat = "identity") + scale_y_continuous(labels = scales::dollar) + 
  scale_fill_manual(name = "Year", values = man.pal) + theme_dark()+
  labs(x = "Year", y = "Sales") + theme(legend.position="none")


year1.ts <- window(all.ts, end = c(years.incl[2],1))
year2.ts <- window(all.ts, start = c(years.incl[2],1))
all.line <- autoplot(all.ts) + autolayer(year1.ts, color = man.pal[1], size = 3) + 
  autolayer(year2.ts, color = man.pal[2], size = 3) + theme_dark()+ 
  labs(y = "Sales", title = "Total Sales from Selected Supplier by Month") +
  scale_y_continuous(labels = scales::dollar)
}

if(length(years.incl) == 3){

all.bar <- ggplot(data = allin.agg, aes(y = Total.Sales, x = factor(Year), fill = factor(Year))) + 
  geom_bar(stat = "identity") + scale_y_continuous(labels = scales::dollar) + 
  scale_fill_brewer(name = "Year", palette = "RdBu") + theme_dark()+
  labs(x = "Year", y = "Sales") + theme(legend.position="none")

man.pal <- c("#ef8a62", "#f7f7f7", "#67a9cf") #manual palette
year1.ts <- window(all.ts, end = c(years.incl[2],1))
year2.ts <- window(all.ts, start = c(years.incl[2],1), end = c(years.incl[3],1))
year3.ts <- window(all.ts, start = c(years.incl[3],1))

all.line <- autoplot(all.ts) + autolayer(year1.ts, color = man.pal[1], size = 3) + 
  autolayer(year2.ts, color = man.pal[2], size = 3) + 
  autolayer(year3.ts, color = man.pal[3], size = 3) + theme_dark() + 
  labs(y = "Sales", title = "Total Sales from Selected Supplier by Month") +
  scale_y_continuous(labels = scales::dollar)

}

if(length(years.incl) == 4){
#c(#ca0020, #f4a582, #92c5de, #0571b0)
  
  all.bar <- ggplot(data = allin.agg, aes(y = Total.Sales, x = factor(Year), fill = factor(Year))) + 
  geom_bar(stat = "identity") + scale_y_continuous(labels = scales::dollar) + 
  scale_fill_brewer(name = "Year", palette = "RdBu") + theme_dark()+
  labs(x = "Year", y = "Sales") + theme(legend.position="none")

man.pal <- c("#ca0020", "#f4a582", "#92c5de", "#0571b0") #manual palette
year1.ts <- window(all.ts, end = c(years.incl[2],1))
year2.ts <- window(all.ts, start = c(years.incl[2],1), end = c(years.incl[3],1))
year3.ts <- window(all.ts, start = c(years.incl[3],1), end = c(years.incl[4],1))
year4.ts <- window(all.ts, start = c(years.incl[4],1))

all.line <- autoplot(all.ts) + autolayer(year1.ts, color = man.pal[1], size = 3) + 
  autolayer(year2.ts, color = man.pal[2], size = 3) + 
  autolayer(year3.ts, color = man.pal[3], size = 3) + 
  autolayer(year4.ts, color = man.pal[4], size = 3) + theme_dark()+ 
  labs(y = "Sales", title = "Total Sales from Selected Supplier by Month") +
  scale_y_continuous(labels = scales::dollar)
}

if(length(years.incl) == 5){
#c(#ca0020, #f4a582, #f7f7f7, #92c5de, #0571b0)
  
  all.bar <- ggplot(data = allin.agg, aes(y = Total.Sales, x = factor(Year), fill = factor(Year))) + 
  geom_bar(stat = "identity") + scale_y_continuous(labels = scales::dollar) + 
  scale_fill_brewer(name = "Year", palette = "RdBu") + theme_dark()+
  labs(x = "Year", y = "Sales") + theme(legend.position="none")

man.pal <- c("#ca0020", "#f4a582", "#f7f7f7","#92c5de", "#0571b0") #manual palette
year1.ts <- window(all.ts, end = c(years.incl[2],1))
year2.ts <- window(all.ts, start = c(years.incl[2],1), end = c(years.incl[3],1))
year3.ts <- window(all.ts, start = c(years.incl[3],1), end = c(years.incl[4],1))
year4.ts <- window(all.ts, start = c(years.incl[4],1), end = c(years.incl[5],1))
year5.ts <- window(all.ts, start = c(years.incl[5],1))

all.line <- autoplot(all.ts) + autolayer(year1.ts, color = man.pal[1], size = 3) + 
  autolayer(year2.ts, color = man.pal[2], size = 3) + 
  autolayer(year3.ts, color = man.pal[3], size = 3) + 
  autolayer(year4.ts, color = man.pal[4], size = 3) +
  autolayer(year5.ts, color = man.pal[5], size = 3) + theme_dark()+ 
  labs(y = "Sales", title = "Total Sales from Selected Supplier by Month") +
  scale_y_continuous(labels = scales::dollar)
}

#autoplot(all.ts) + theme_dark() + geom_line(aes(color = Year), size = 4) + scale_color_brewer(palette = "RdBu")



```

## Summary
**For the selected time period there were `r prod.uniq` distinct `r supplier.to.dive`  products (SKUs) sold in `r cat.uniq` categories across `r dept.uniq` department(s).**

## Bar Graph of Sales from `r supplier.to.dive` by Year

```{r, echo=FALSE}
print(all.bar)
print(all.line)

```

## Line Graph of Sales by Category

```{r categories, echo=FALSE}
cats <- ggplot(cat.agg, aes(x = Year, fill = Category)) +
  geom_col(aes(y = Total.Sales), position = "dodge")

cats.line <- ggplot(cat.agg, aes(x = Year, color = Category)) +
  geom_line(aes(y = Total.Sales), size = 3) + 
  theme_dark() + labs(y = "Sales", title = paste("Sales by Category for", supplier.to.dive)) +
  scale_y_continuous(labels = scales::dollar)
print(cats.line)

cat.agg.pretty <- cat.agg
cat.agg.pretty$Total.Sales <- paste0("$",prettyNum(round(cat.agg.pretty$`Total.Sales`), big.mark = ","))
```

### Sales by Category in Dollars

```{r category.sales, echo=FALSE}
cat.2018 <- cat.agg.pretty %>% filter(Year == 2018) %>% select(2,4) %>% rename("2018" = Total.Sales)
cat.2017 <- cat.agg.pretty %>% filter(Year == 2017) %>% select(2,4) %>% rename("2017" = Total.Sales)
cat.2016 <- cat.agg.pretty %>% filter(Year == 2016) %>% select(2,4) %>% rename("2016" = Total.Sales)
cat.2015 <- cat.agg.pretty %>% filter(Year == 2015) %>% select(2,4) %>% rename("2015" = Total.Sales)

cat.kable <- merge(cat.2018, cat.2017)
cat.kable <- merge(cat.kable, cat.2016)
cat.kable <- merge(cat.kable, cat.2015)
kable(cat.kable)
```

### Sales by Category in Units Sold

```{r units.sales, echo = FALSE}
cat.2018.unit <- cat.unit %>% filter(Year == 2018) %>% select(2,4) %>% rename("2018" = Total.Sales)
cat.2017.unit <- cat.unit %>% filter(Year == 2017) %>% select(2,4) %>% rename("2017" = Total.Sales)
cat.2016.unit <- cat.unit %>% filter(Year == 2016) %>% select(2,4) %>% rename("2016" = Total.Sales)
cat.2015.unit <- cat.unit %>% filter(Year == 2015) %>% select(2,4) %>% rename("2015" = Total.Sales)

cat.kable.unit <- merge(cat.2018.unit, cat.2017.unit)
cat.kable.unit <- merge(cat.kable.unit, cat.2016.unit)
cat.kable.unit <- merge(cat.kable.unit, cat.2015.unit)

kable(cat.kable.unit)

```

\newpage

## How Individual `r supplier.to.dive` Products Sold in `r year(as.Date(max(data.clean$Date.Sold, na.rm = TRUE)))` vs. Prior Years

```{r, echo=FALSE, fig.height=6}
product.agg.cy <- rename(product.agg.cy, "Product" = Description)
product.agg.py <- filter(product.agg, Year == py)
product.merge.py <- product.agg.py[,c(2,4)]
colnames(product.merge.py) <- c("Product", "Prior Yr")
product.merge <- merge(product.agg.cy, product.merge.py, by.x="Product", all.x=TRUE, all.y=FALSE)
product.merge <- mutate(product.merge, "Growth" = Total.Sales - `Prior Yr`, "Perc.Growth" = 
                      paste0(round((Growth/`Prior Yr`)*100,1),"%")) %>%
  arrange(desc(Total.Sales)) %>%
  select(1,4:8)
colnames(product.merge)[c(2,4)] <- c("Sales Current Yr", "Sales Prior Yr")
product.merge[is.na(product.merge)] <- 0

# supplier calcs retain to avoid dependency errors from dependencies on variable names
supplier.agg.py <- filter(supplier.agg, Year == py)
sup.merge.py <- supplier.agg.py[,c(2,4)]
colnames(sup.merge.py) <- c("Supplier", "Prior Yr")
sup.merge <- merge(supplier.agg.cy, sup.merge.py, by.x="Supplier", all.x=TRUE, all.y=FALSE)
sup.merge <- mutate(sup.merge, "Growth" = Total.Sales - `Prior Yr`, "Perc.Growth" = 
                      paste0(round((Growth/`Prior Yr`)*100,1),"%")) %>%
  arrange(desc(Total.Sales)) %>%
  select(1,4:8)
colnames(sup.merge)[c(2,4)] <- c("Sales Current Yr", "Sales Prior Yr")
sup.merge[is.na(sup.merge)] <- 0

how.many.in.top <- 15 #select how many should be in plot, contingent on # of years
product.top.cy.vec <- unique(product.merge$Product)[1:how.many.in.top]
product.agg.top <- product.agg[product.agg$Description %in% product.top.cy.vec,]

### sup.yy here
#sup.top10.cy.vec <- unique(sup.merge$Supplier)[1:10]
#supplier.agg.10 <- supplier.agg[supplier.agg$Supplier %in% unique(sup.merge$Supplier)[1:10],]
#print(sup.top10.cy.vec)

#horizontal bar chart showing top 10 Suppliers year over year
g <- ggplot(data = product.agg.top, aes(x = Product.By.Year, fill = factor(Year))) + 
  geom_bar(stat = "identity", aes(y = Total.Sales)) + coord_flip() +
  scale_y_continuous(labels = scales::dollar) +
  scale_fill_brewer(direction = 1, palette = "RdBu", name = "Year") + theme_dark() + 
  labs(title = "Sales From Top Products By Year", y = "Total Sales", x = "Product By Year") 
print(g)

```



```{r product_kable, echo=FALSE}
#product kable calcs
kable.how.many.in.top <- 100
product.agg.cy.pretty <- product.merge
product.agg.cy.pretty$Perc.Whole <- paste0(product.agg.cy.pretty$Perc.Whole, "%")
product.agg.cy.pretty$Growth <- paste0("$",prettyNum(round(product.agg.cy.pretty$Growth), big.mark = ","))
product.agg.cy.pretty$`Sales Prior Yr` <- paste0("$",prettyNum(round(product.agg.cy.pretty$`Sales Prior Yr`), big.mark = ","))
product.agg.cy.pretty$`Sales Current Yr` <- paste0("$",prettyNum(round(product.agg.cy.pretty$`Sales Current Yr`), big.mark = ",")) ## Switch back
if(nrow(product.agg.cy.pretty) < kable.how.many.in.top){
  kable.products <- product.agg.cy.pretty
} else {
  kable.products <- product.agg.cy.pretty[1:kable.how.many.in.top,]
}


#retain supplier calcs to avoid errors
#supplier.agg.cy.pretty <- sup.merge
#supplier.agg.cy.pretty$Perc.Whole <- paste0(supplier.agg.cy.pretty$Perc.Whole, "%")
#supplier.agg.cy.pretty$Growth <- paste0("$",prettyNum(round(supplier.agg.cy.pretty$Growth), big.mark = ","))
#supplier.agg.cy.pretty$`Sales Prior Yr` <- paste0("$",prettyNum(round(supplier.agg.cy.pretty$`Sales Prior Yr`), big.mark = ","))
#supplier.agg.cy.pretty$`Sales Current Yr` <- paste0("$",prettyNum(round(supplier.agg.cy.pretty$`Sales Current Yr`), big.mark = ",")) ## Switch back
#if(nrow(supplier.agg.cy.pretty) < 25){
#  kable.suppliers <- supplier.agg.cy.pretty
#} else {
#  kable.suppliers <- supplier.agg.cy.pretty[1:25,]
#}
```

##Table of Sales by Product Comparing `r cy` with `r py` for Top `r kable.how.many.in.top` Products

Note: "Perc.Whole" means what percentage of all `r supplier.to.dive` sales in `r cy` came from this product

```{r, echo=FALSE}
kable(kable.products)
```


```{r, echo=FALSE}
## Who are the SMALLEST 25% of Suppliers?
#sup.merge <- arrange(sup.merge, `Sales Current Yr`)
#supplier.agg.cy.pretty.b <-  sup.merge   #supplier.agg.cy.bottom
#supplier.agg.cy.pretty.b$Perc.Whole <- paste0(supplier.agg.cy.pretty.b$Perc.Whole, "%")
#supplier.agg.cy.pretty.b$`Sales Current Yr` <-paste0("$",prettyNum(round(supplier.agg.cy.pretty.b$`Sales Current Yr`), big.mark = ","))
#supplier.agg.cy.pretty.b$`Sales Prior Yr` <-paste0("$",prettyNum(round(supplier.agg.cy.pretty.b$`Sales Prior Yr`), big.mark = ","))
#supplier.agg.cy.pretty.b$Growth <-paste0("$",prettyNum(round(supplier.agg.cy.pretty.b$Growth), big.mark = ","))
#kable(supplier.agg.cy.pretty.b[1:109,])

####
# for inline in next title
#top.sup1 <- supplier.agg.cy$Supplier[1]
#top.sup2 <- supplier.agg.cy$Supplier[2]
#top.sup3 <- supplier.agg.cy$Supplier[3]
```

```{r, sup1, echo=FALSE, message=FALSE, warning=FALSE}

#sup1.df <- data.clean[data.clean$Supplier == supplier.agg.cy$Supplier[1],]

#sup1.ts <- exploratory.jh.time.series(sup1.df, freq = 12)

#autoplot(sup1.ts) + theme_dark() + geom_line(color = "#67a9cf", size = 4)+ labs(y = "Sales") +
#  scale_y_continuous(labels = scales::dollar)

#exploratory.top.three.prod.ts <- function(supplier.filter, df.to.use){
  
#  require(dplyr)
#  require(fpp2)
#  exploratory.jh.time.series <- function(clean.df, freq = 365){
#    require(lubridate)
#    require(dplyr)
#    clean.df <- arrange(clean.df, Date.Sold)
#    clean.df$Day <- date(clean.df$Date.Sold) # df should have been arranged in cleaning step
##    start.year <- year(clean.df$Day)[1]
#    if(freq == 365){
#      start.day <- date(head(clean.df$Day,1)) - floor_date(head(clean.df$Day,1), unit = "year")+1 # subtracts earliest day from first day of year plus one
#      sales.agg <- aggregate(Total.Sales ~ Day, clean.df, sum)
#      all.dates <- seq.Date(from = as.Date(min(sales.agg$Day, na.rm = TRUE)), to = as.Date(max(sales.agg$Day, na.rm = TRUE)),by = 1)
##      sales.agg.all <- left_join(data.frame(Day = all.dates), sales.agg)
#      sales.ts <- ts(sales.agg.all$Total.Sales, start = c(start.year, start.day), frequency = 365)
#    }
#    if(freq == 12){
#      start.month <- month(head(clean.df$Month,1))
#      sales.agg <- aggregate(Total.Sales ~ Month + Year, clean.df, sum)
      #print(head(sales.agg, 25))
#      sales.agg.all <- left_join(sales.agg, data.frame(Month = 1:12))
#      sales.ts <- ts(sales.agg.all$Total.Sales, start = c(start.year, start.month), frequency = 12)
#    }
#    sales.ts[is.na(sales.ts)] <- 0
    
#    sales.ts
#  }
  
#  df.one.supplier <- filter(df.to.use, Supplier == supplier.filter)
#  agg.by.prod <- aggregate(Total.Sales ~ Description, df.one.supplier, sum)
#  agg.by.prod <- arrange(agg.by.prod, desc(Total.Sales))
#  top.prods <- agg.by.prod[c(1,2,3), 1]
  
#  prod1 <- filter(df.one.supplier, Description == top.prods[1])
#  prod1.ts <- exploratory.jh.time.series(prod1, freq = 12)
  #print(head(prod1.ts))
  
#  prod2 <- filter(df.one.supplier, Description == top.prods[2])
#  prod2.ts <- exploratory.jh.time.series(prod2, freq = 12)
  
#  prod3 <- filter(df.one.supplier, Description == top.prods[3])
#  prod3.ts <- exploratory.jh.time.series(prod3, freq = 12)
  
#  joint.ts <- ts.union(prod1.ts, prod2.ts, prod3.ts)
#  colnames(joint.ts) <- top.prods
  #joint.length <- nrow(joint.ts)
  #print(joint.length)
  #label.vec <- seq(from = "1", to = joint.length, by = 3)
  #print(label.vec)
  
  #create labels and breaks
#3  df.to.use <- arrange(df.to.use, Date.Sold)
#3  df.to.use <- df.to.use[!is.na(df.to.use$Date.Sold),]
#  df.to.use$Day <- date(df.to.use$Date.Sold)
#  start.year <- year(df.to.use$Day)[1]
#3  end.year <- year(df.to.use$Day[length(df.to.use$Day)])

#  autoplot(joint.ts) +
#theme_dark() + theme(legend.position = "top") + geom_line(size = 2) + scale_color_brewer(direction = -1) + 
#    scale_x_continuous(breaks = seq(from = start.year, to = end.year, by = 1)) + 
#    labs(y = "Sales", title = paste0("Monthly Sales for the Top 3 Products from ", supplier.filter)) +
#           scale_y_continuous(labels = scales::dollar)
  #joint.df <- data.frame(Y=as.matrix(joint.ts), date=time(joint.ts))
  #ggplot(data = joint.df, aes(x = data))

#}

#exploratory.top.three.prod.ts(top.sup1, data.clean)

```
