---
title: "Staffing Analysis"
author: "Allocate Analytics"
date: "March 16, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(ggplot2)
library(sugrrants)
library(lubridate)
library(prophet)

#data4years <- read.csv("mutated.data1417.csv", stringsAsFactors = FALSE)

#####
data4years <- read.csv("data/sample data/fake.wt.fixed2.csv", stringsAsFactors = FALSE)


#####
data4years <- filter(data4years, Register != "9")

data4years.wide <- data4years
data4years.wide$Date.Sold <- as_date(data4years.wide$Date.Sold)
#data4years.wide$Date.Sold.Round <- floor_date(data4years.wide$Date.Sold, unit = "hour")
data4years.wide$Date.Sold <- as_date(data4years.wide$Date.Sold)
data4years.wide$Date.Sold.Round <- as_datetime(data4years.wide$Date.Sold.Round)

data17 <- filter(data4years.wide, Year == 2017)
#print(str(data17))
#print(head(data17))

data17.agg <- aggregate(Total.Sales ~ Date.Sold.Round + Date.Sold, data17, sum)
data17.agg <- data17.agg %>%
  mutate("Hour" = as.integer(hour(Date.Sold.Round))) %>%
  frame_calendar(x = Hour, y = Total.Sales, date = Date.Sold, calendar = "monthly")
data17.plot <- data17.agg %>%
  ggplot(aes(x = .Hour, y = .Total.Sales, group = Date.Sold)) + geom_line()

```

```{r calendar.17.plot, echo=FALSE}
print(unique(data4years$Register))
prettify(data17.plot)
```

## Comments and Trends

1 Almost no big days until 2nd weekend of April and hen it's Fri, Sat, Sun
2 Weekdays start getting consistently big after Memorial Day
3 Weekdays slow down after Labor Day
4 October weekdays even slower than Sept.
5 Beginning around Halloween Saturday is really the main big weekend day until the week before Xmas and except for Thanksgiving weekend


```{r calendar.16.plot, echo=FALSE}
data16 <- filter(data4years.wide, Year == 2016)

data16.agg <- aggregate(Total.Sales ~ Date.Sold.Round + Date.Sold, data16, sum)
data16.agg <- data16.agg %>%
  mutate("Hour" = as.integer(hour(Date.Sold.Round))) %>%
  frame_calendar(x = Hour, y = Total.Sales, date = Date.Sold, calendar = "monthly")
data16.plot <- data16.agg %>%
  ggplot(aes(x = .Hour, y = .Total.Sales, group = Date.Sold)) + geom_line()
prettify(data16.plot)

```


### Off Peak Minimum Staffing

```{r off.peak.minimum, echo=FALSE}

data2years.wide <- filter(data4years.wide, Year %in% c(2016, 2017))

#data2years$Date.Sold <- as_date(data2years$Date.Sold)

data2years.wide <- data2years.wide %>%
  mutate("Hour" = hour(Date.Sold.Round)) %>%
  mutate("Weekday" = wday((Date.Sold.Round)))
    
# filter for off.peak.minimum ##
df1 <- data2years.wide %>%
  filter(Date.Sold >= "2016-01-01", Date.Sold <= "2016-01-31")
df2 <- data2years.wide %>%
  filter(Date.Sold >= "2016-02-01", Date.Sold <= "2016-04-07", Weekday %in% c(1, 2, 3, 4, 5, 7))

print(head(df2))
print(tail(df2))

df.all <- rbind(df1, df2)

# need to go back to original script and add additional start dates with defaults like 0 for min and 100000 for max
staffing.day.plot.2 <- function(df, nickname.of.time.range){
  
  library(lubridate)
  library(dplyr)
  library(ggplot2)
  
  df.agg <- aggregate(Total.Sales ~ Date.Sold.Round + Hour + Weekday, df.all, sum)
  conf.df <- data.frame()
  
  for(i in 9:23){
    print(i)
    i.hour.vec <- df.agg %>%
      filter(Hour == i) %>%
      select(Total.Sales)
    #i.hour.vec <- as.double(i.hour.vec)
    print(head(i.hour.vec))
    #i.estimate.95 <- t.test(i.hour.vec, conf.level = 0.95)$estimate
    #i.conf.int.95 <- t.test(i.hour.vec, conf.level = 0.95)$conf.int
    #i.conf.int.75 <- t.test(i.hour.vec, conf.level = 0.75)$conf.int
    #i.conf.int.50 <- t.test(i.hour.vec, conf.level = 0.50)$conf.int
    #three.conf.int <- c(i, i.estimate.95, i.conf.int.95, i.conf.int.75, i.conf.int.50)
    quantiles <- quantile(as.numeric(unlist(i.hour.vec)), probs = c(.5, .025, .975, .125, .875, .25, .75))
    print(class(quantiles))
    
    quantiles.hour <- c(i, quantiles)
    print(class(quantiles.hour))
    conf.df <- rbind(conf.df, quantiles.hour)
    
    #i.estimate.95 <- quantie(i.hour.vec, .5)
    #i.conf.int.95.high <- 
    #quantiles.hour <- c(i, quantile(i.hour.vec, c(.5, .025, .975, .125, .875, .25, .75)))
  }
    colnames(conf.df) <- c("hour", "estimate", "low95", "high95", "low75", "high75", "low50", "high50")
    
    day.plot <- ggplot(data = conf.df, aes(x=hour)) +
      geom_ribbon(aes(ymin=low95, ymax=high95), fill="#0571b0", alpha = .75)+
      geom_ribbon(aes(ymin=low75, ymax=high75), fill="#92c5de", alpha = .75)+
      geom_ribbon(aes(ymin=low50, ymax=high50), fill="#d1e5f0", alpha = .75)+
      geom_ribbon(aes(ymin=estimate-20, ymax=estimate+20), fill="#ef8a62")
    print(day.plot)
}

#staffing.day.plot.2(df.all)


```

```{r peak.6.days, echo=FALSE}

# filter for off.peak.minimum ##
df1 <- data2years.wide %>%
  filter(Date.Sold >= "2016-06-25", Date.Sold <= "2016-09-03", Weekday %in% c(1, 2, 3, 4, 5, 6))
df2 <- data2years.wide %>%
  filter(Date.Sold >= "2017-06-25", Date.Sold <= "2017-09-03", Weekday %in% c(1, 2, 3, 4, 5, 6))

#print(head(df2))
#print(tail(df2))

df.all <- rbind(df1, df2)
staffing.day.plot.2(df.all)


```


### Prophet Trends


```{r, echo=FALSE}

require(prophet)

data1617 <- rbind(data16, data17) #filter(data4years, Year %in% c(2016, 2017))
data1617.peak <- filter(data1617, Month %in% c(6, 7, 8))
data1617.agg <- aggregate(Total.Sales ~ Date.Sold.Round, data1617.peak, sum)
#print(head(data1617.agg, 100))
colnames(data1617.agg) <- c("ds", "y")
model <- prophet(data1617.agg, yearly.seasonality = TRUE, daily.seasonality = TRUE)
future <- make_future_dataframe(model, periods = 365)
forecast <- predict(model, future)
#prophet.plot.obj <- prophet_plot_components(model, forecast)
#print(prophet.plot.obj[[4]])

#data.date.agg <- aggregate(Total.Sales ~ Date + Supplier, data.both, sum)
#colnames(data.date.agg) <- c("ds", "Supplier", "y")
#prophet.data <- filter(data.date.agg, Supplier == supplier.name)
#print(head(prophet.data, 10))
#prophet.data <- select(prophet.data, ds, y)
#model <- prophet(prophet.data, yearly.seasonality = TRUE)
#future <- make_future_dataframe(model, periods = 365)
#forecast <- predict(model, future)
#prophet.plot.obj <- prophet_plot_components(model, forecast)
#print(prophet.plot.obj)


```




```{r, echo=FALSE}

# write a script that will compute in table and plot the shape of the day with uncertainty included




