---
title: "Jewelry Order Value at Whale's Tale & Splash"
author: "Sam Pritchard - Allocate Analytics"
date: "February 24, 2019"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#next fix the text

require(dplyr)
require(ggplot2)
require(knitr)
require(ggridges)

setwd("C://Users/The Pritchard family/Documents/R/wt_gh/")

import.jh.sql.connect <- function(db.name.in.sql.server){
  library(odbc)
  library(DBI)
  
  con <- DBI::dbConnect(odbc::odbc(),
                        Driver = "SQL Server",
                        Server = "LAPTOP-JHRVTF04\\SQLEXPRESS",
                        Database = db.name.in.sql.server,
                        Trusted_Connection = "True")
  con
}

import.jh.detailed.sales <- function(){
  joined.df <- DBI::dbGetQuery(con,'
                                SELECT TransactionEntry.ItemID, TransactionEntry.Price, 
                                 TransactionEntry.TransactionTime, TransactionEntry.Quantity, 
                                  TransactionEntry.TransactionNumber, Item.Description, 
                                 Department.Name AS "Department", Category.Name AS "Category", 
                                 SupplierName AS "Supplier", Cashier.Name AS "CashierName", 
                                 Register.Number AS "Register", Register.Description AS "RegLocation"

                                 FROM TransactionEntry
                                 
                                 JOIN Item ON TransactionEntry.ItemID = Item.ID
                                 JOIN Department ON Item.DepartmentID = Department.ID
                                 JOIN Category ON Item.CategoryID = Category.ID
                                 JOIN Supplier ON Item.SupplierID = Supplier.ID
                                 JOIN [Transaction] ON TransactionEntry.TransactionNumber = [Transaction].TransactionNumber
                                 JOIN Batch ON [Transaction].BatchNumber = Batch.BatchNumber
                                 JOIN Register ON Batch.RegisterID = Register.ID
                                 JOIN Cashier ON [Transaction].CashierID = Cashier.ID')
  joined.df
  }

clean.jh.detailed.sales <- function(sql.df){
  library(dplyr)
  library(lubridate)
    
    sql.df <- sql.df %>%
      rename(Sold.Price = Price, Cashier = CashierName, Date.Sold = TransactionTime,
             Qty.Sold = Quantity, Transaction = TransactionNumber) %>%
      mutate(Total.Sales = Qty.Sold*Sold.Price) %>%
      select(Department, Category, Supplier, ItemID, Description, Qty.Sold, Sold.Price, 
             Total.Sales, Transaction, Date.Sold, Register, Cashier)
    
    sql.df$Date.Sold <- ymd_hms(sql.df$Date.Sold)
    sql.df$Year <- year(sql.df$Date.Sold)
    sql.df$Month <- month(sql.df$Date.Sold)
    sql.df$Department <- trimws(sql.df$Department)
    sql.df$Category <- trimws(sql.df$Category)
    sql.df$Supplier <- trimws(sql.df$Supplier)
    sql.df$Item <- trimws(sql.df$Item)
    #print(head(sql.df))
    sql.df$Dept.By.Year <- paste(sql.df$Department, sql.df$Year)
    sql.df$Categ.By.Year <- paste(sql.df$Category, sql.df$Year)
    sql.df
}

if(file.exists(paste0("data/sales.data.cache", Sys.Date(), ".csv"))){
  data.clean <- read.csv(paste0("data/sales.data.cache", Sys.Date(), ".csv"), stringsAsFactor = FALSE)
} else {
con <- import.jh.sql.connect("WHALESTALE")

new.df <- import.jh.detailed.sales() # uses con but not as argument

data.clean <- clean.jh.detailed.sales(new.df)

write.csv(data.clean, paste0("data/sales.data.cache", Sys.Date(), ".csv"), row.names = FALSE)
}

data.clean <- filter(data.clean, Year == 2018)
wt.jewel <- filter(data.clean, Department == "JEWELRY", Register != 9)
splash.jewel <- filter(data.clean, Department == "JEWELRY", Register == 9)

#read in data
#mutated.four.years <- read.csv("mutated.data1417.csv", stringsAsFactors = FALSE)
#mutated.four.years <- read.csv("/srv/shiny-server/ab-trail/mutated.data1417.csv", stringsAsFactors = FALSE)

#read in functions
cart.mean.all <- function(dataset){
  require(ggplot2)
  require(dplyr)
  #require(xts)
  require(lubridate)
  require(scales)
  
  dataset$row.count = 1
  dataset <- dataset %>%
    mutate("Year.Mo" = as_date(paste(substr(Date.Sold, 1,7),"-01"),ymd))
  data.agg <- aggregate(Total.Sales ~ Transaction + Year.Mo, dataset, sum)
  data.mean <- aggregate(Total.Sales ~ Year.Mo, data.agg, mean)

  #print(head(dataset))
  data.item.agg <- aggregate(row.count ~ Transaction + Year.Mo, dataset, length)
  data.length <- aggregate(row.count ~ Year.Mo, data.item.agg, mean)
  #print(data.length)
  data.length$row.count <- as.numeric(data.length$row.count)
  data.cols <- merge(data.mean, data.length)
  data.cols$Item.Value <- data.cols$Total.Sales/data.cols$row.count
  #print(data.cols)
  cart <- ggplot(data = data.cols, aes(x=Year.Mo, group = 1)) + geom_line(aes(y=Total.Sales), color = "purple", size = 2) + 
    geom_line(aes(y=row.count*5.56), color = "red", size = 2) + geom_line(aes(y=Item.Value), color = "blue", size = 2) + 
    scale_y_continuous(labels = dollar, sec.axis = sec_axis(~./5.56, name = "Number of Items Purchased"), limits = c(0, NA)) +
    labs(y = "$ of Avg Cart Size & Item Size", x = "Years By Month", title= "4 Years of Cart Sizes & Components")

  cart
}

cart.mean <- function(dataset){
  require(ggplot2)
  data.agg <- aggregate(Total.Sales ~ Transaction + Month, dataset, sum)
  data.mean <- aggregate(Total.Sales ~ Month, data.agg, mean)
  #print(head(data.mean, 12))
  data.mean$Month <- as.factor(data.mean$Month)
  cart <- ggplot(data = data.mean, aes(x=Month, y=Total.Sales)) + geom_line()
  cart
}

cart.hist <- function(dataset){
  require(ggplot2)
  require(plotly)
  data.agg <- aggregate(Total.Sales ~ Transaction + Month, dataset, sum)
  
  gg.hist <- ggplot(data = data.agg, aes(Total.Sales)) + geom_histogram(binwidth = 5, color = "grey", fill = "blue")
  gg.hist <- gg.hist + xlim(0, 120) + theme_dark()
  #plotly.hist <- ggplotly(gg.hist)
  #plotly.hist
  gg.hist
}

cart.items <- function(dataset){
  require(ggplot2)
  dataset$row.count = 1
  data.agg <- aggregate(row.count ~ Transaction + Month, dataset, length)
  data.length <- aggregate(row.count ~ Month, data.agg, mean)
  
  print(head(data.agg))
  print(data.length)
}

item.hist <- function(dataset){
  require(ggplot2)
  require(plotly)
  #data.agg <- aggregate(Total.Sales ~ Transaction + Month, dataset, sum)
  #92c5de
  #0571b0#f4a582
  gg.hist <- ggplot(data = dataset, aes(Total.Sales)) + geom_histogram(binwidth = 25, color = "black", fill = "#92c5de")
  gg.hist <- gg.hist + xlim(0, 500) + theme_dark() + labs(x = "Price Point of Jewelry Item", y = "Jewelry Items Sold in 2018")
  #plotly.hist <- ggplotly(gg.hist)
  #plotly.hist
  gg.hist
}

item.ridges <- function(dataset.a, dataset.b, name.a = "Whale's Tale", name.b = "Splash"){
  dataset.a <- cbind(dataset.a, "Store" = name.a)
  dataset.b <- cbind(dataset.b, "Store" = name.b)
  dataset.all <- rbind(dataset.b, dataset.a)
  dataset.all <- filter(dataset.all, Total.Sales >0, Total.Sales <= 500)
  
  ggcompare <- ggplot(data = dataset.all, aes(x = Total.Sales, y = Store, fill = Store)) + 
    geom_density_ridges() + scale_fill_manual(values = c("#f4a582","#92c5de")) + 
    scale_x_continuous(labels = scales::dollar) + 
    labs(x = "Price Point of Jewelry Item", y = "Jewelry Items Sold in 2018") + theme_dark()
  ggcompare
  #print(head(dataset.a))
  #print(head(dataset.b))
}

aov.kable <- function(dataset.a, dataset.b, threshold = 150, name.a = "Whale's Tale", name.b = "Splash"){
  mean.a <- paste0("$",round(mean(dataset.a$Total.Sales),2))
  over.thresh.a <- filter(dataset.a, Total.Sales >= threshold)
  under.thresh.a <- filter(dataset.a, Total.Sales < threshold)
  over.perc.a <- paste0(round((nrow(over.thresh.a)/nrow(dataset.a))*100,1),"%")
  under.perc.a <- paste0(round((nrow(under.thresh.a)/nrow(dataset.a))*100,1),"%")
  over.perc.dollar.a <- paste0(round((sum(over.thresh.a$Total.Sales)/sum(dataset.a$Total.Sales))*100,1),"%")
  under.perc.dollar.a <- paste0(round((sum(under.thresh.a$Total.Sales)/sum(dataset.a$Total.Sales))*100,1),"%")
  
  mean.b <- paste0("$",round(mean(dataset.b$Total.Sales),2))
  over.thresh.b <- filter(dataset.b, Total.Sales >= threshold)
  under.thresh.b <- filter(dataset.b, Total.Sales < threshold)
  over.perc.b <- paste0(round((nrow(over.thresh.b)/nrow(dataset.b))*100,1),"%")
  under.perc.b <- paste0(round((nrow(under.thresh.b)/nrow(dataset.b))*100,1),"%")
  over.perc.dollar.b <- paste0(round((sum(over.thresh.b$Total.Sales)/sum(dataset.b$Total.Sales))*100,1),"%")
  under.perc.dollar.b <- paste0(round((sum(under.thresh.b$Total.Sales)/sum(dataset.b$Total.Sales))*100,1),"%")
  
  
aov.table <- data.frame("Store" = c(name.a, name.b),"Avg Price" = c(mean.a, mean.b), "Trans Over" = c(over.perc.a, over.perc.b),
                        "Trans Under" = c(under.perc.a, under.perc.b), "$ Over" = c(over.perc.dollar.a, over.perc.dollar.b), 
                        "$ Under" = c(under.perc.dollar.a, under.perc.dollar.b))  
colnames(aov.table) <- c("Store", "Avg Price", "Trans Over", "Trans Under", "$ Over", "$ Under")
kable(aov.table)

}
```

## Headline:
### The hypothesis that higher priced jewelry (over $150) doesn't sell very often at Whale's Tale is largely true.  Of the jewelry pieces that sold at Whale's Tale in 2018, only 2.7% had a price at $150 or more compared with 18.8% at Splash.  The percentage is higher measured by dollars: 13.3% of the jewelry dollars at Whale's Tale came from pieces over $150 while 49.6% of Splash jewelry dollars came from pieces at or over $150.

The table below includes the numbers mentioned above plus the average price of jewelry sold at each store.

The plots illustrate the price points of jewelry sold at each store.  The first one shows both stores side-by-side for easy comparison.

The later ones with light blue bars shows one store at a time and break up the categories more cleanly.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#print(dim(mutated.four.years))

#cart.mean.all(mutated.four.years)
aov.kable(wt.jewel, splash.jewel)
```

## Comparison of Jewelry Order Value at Whale's Tale and Splash
```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=4}
item.ridges(wt.jewel, splash.jewel)
```

## Jewelry Order Value at Whale's Tale in $25 Increments
Note: The bar directly above a number covers from that number to $25 less.  For example the bar directly over $100 covers $75-$100

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=3.5, fig.width=6}
item.hist(wt.jewel)
```

## Jewelry Order Value at Splash in $25 Increments

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=3.5, fig.width=6}
item.hist(splash.jewel)
```

